Bayesian Evidence Synthesis:opioid crisis

### 2020-04-12 latex/researchpaper.tex
latex editing ongoing before simulation

\normalsize
[\textbf{phrase differently: the prior and the data relate to "all the unknown parameter", but as a last stage you focus on one target.}]\\

[\textbf{following the comment, the first attempt:}]\\  
The number of overdoses is our ultimate target of estimation. To achieve the goal in context of Bayesian statistics, we use our prior belief and available data set about the target of estimation. The posterior belief is coming from both of these sources of the information. Let $\theta$ denote all the unknown variables and let $Y$ denote all the related data sets. The following equation express the idea of Bayesian generative models in a mathmatical form:
\begin{equation}
\label{generic_bayes_thm}
\left.\begin{aligned}
p(\theta| Y ) = \frac{ p(\theta, Y)   }{ p(y)} = \frac{ p(\theta) p(Y|\theta)}{ p(Y)} \propto p(\theta) p(Y| \theta) \end{aligned}\right.
\end{equation}
[\textbf{Question: to make this flow better, maybe you want a  version of (1) which generically describes parameter and latent varaibles given observed data.}]
where $p(\cdot)$ is probability density (or mass) function. The equation \ref{generic_bayes_thm} states that the posterior belief of unobserved variables, $p(\theta|Y)$, is proportional to the mixture of the prior belief of the varaibles, $p(\theta)$, and the related data sets given the prior belief, $p(Y|\theta)$. Notice that the vector $\theta$ from equation \ref{generic_bayes_thm} includes parameters and latent variables, and hence it contains the total number of overdoses.

@@

[\textbf{draft:}] A generative model described in figure \ref{simple_draw} at a month $t$ can be written as follows given some a priori assumptions:

\begin{equation}
\label{gen_model}
\left.\begin{aligned}
p(\theta) & =p(\mu,\sigma^2,\lambda_t, N, O_t, p_{A,t}, n_{A,t}, x_{A,t}, U_t) \\
& = p(\mu)p(\sigma^2)p(\lambda_t|\mu, \sigma^2)p(N)p(O_t|\lambda_t, N)p(p_{A,t})p(n_{A,t})p(x_{A,t}|p_{A,t},n_{A,t})p(U_t|O_t, p_{A,t}) \\
& \propto p(\mu)p(\sigma^2)p(\lambda_t|\mu, \sigma^2)p(O_t|\lambda_t, N)p(p_{A,t})p(x_{A,t}|p_{A,t},n_{A,t})p(U_t|O_t, p_{A,t}) 
 \end{aligned}\right.
\end{equation}

@@

\bibliographystyle{unsrt}
\bibliography{sample.bib}
\end{document}

>>>>

\normalsize
[\textbf{I guess its done; phrase differently: the prior and the data relate to "all the unknown parameter", but as a last stage you focus on one target.}]\\

[\textbf{done?; following the comment, the first attempt:}]\\  
The number of overdoses is our ultimate target of estimation. To achieve the goal in context of Bayesian statistics, we use our prior belief and available data set about the target of estimation. The posterior belief is coming from both of these sources of the information. Let $\theta$ denote all the unknown variables and let $Y$ denote all the related data sets. The following equation express the idea of Bayesian generative models in a mathmatical form:
\begin{equation}
\label{generic_bayes_thm}
\left.\begin{aligned}
p(\theta| Y ) = \frac{ p(\theta, Y)   }{ p(y)} = \frac{ p(\theta) p(Y|\theta)}{ p(Y)} \propto p(\theta) p(Y| \theta) \end{aligned}\right.
\end{equation}
[\textbf{done?: to make this flow better, maybe you want a  version of (1) which generically describes parameter and latent varaibles given observed data.}]
where $p(\cdot)$ is probability density (or mass) function. The equation \ref{generic_bayes_thm} states that the posterior belief of unobserved variables, $p(\theta|Y)$, is proportional to the mixture of the prior belief of the varaibles, $p(\theta)$, and the related data sets given the prior belief, $p(Y|\theta)$. Notice that the vector $\theta$ from equation \ref{generic_bayes_thm} includes parameters and latent variables, and hence it contains the total number of overdoses.

@@

[\textbf{done?: mentioning how generative model factors and mentioning fig 1 again.}] A generative model described in figure \ref{simple_draw} at a month $t$ can be written as follows given some a priori assumptions:

\begin{equation}
\label{gen_model}
\left.\begin{aligned}
p(\theta) & =p(\mu,\sigma^2,\lambda_t, N, O_t, p_{(A,t)}, n_{(A,t)}, x_{(A,t)}, U_t) \\
& = p(\mu)p(\sigma^2|\mu)p(\lambda_t|\mu, \sigma^2)p(N)p(O_t|\lambda_t, N)p(p_{(A,t)})p(n_{(A,t)})p(x_{(A,t)}|p_{(A,t)},n_{(A,t)})p(U_t|O_t, p_{(A,t)}) \\
& \propto p(\mu)p(\sigma^2)p(\lambda_t|\mu, \sigma^2)p(O_t|\lambda_t, N)p(p_{(A,t)})p(x_{(A,t)}|p_{(A,t)},n_{(A,t)})p(U_t|O_t, p_{(A,t)}) 
 \end{aligned}\right.
\end{equation}

The chain rule for random variables \cite{chain_rule} is used to the joint distribution of all variables at the first line of equation \ref{gen_model} such that the second line of the equation is derived.
A priori independence assumptions and conditional independence assumptions were presumed so that the second line of the equation is simplified. For example, it is asumed that  $\sigma^2$ and $\mu$ are independent to each other and $p_{A,t}$ and also all the variables from overdose model \ref{overdose}, ($\mu, \sigma^2, \lambda_t, N, O_t$), are independent to each other. 
Note that as a function of unknown variables, the function from the second line of the equation \ref{gen_model} is proportional to the function from the third line of the equation since $N$ and $n_{(A,t)}$ are presumed to be known and constants such that the density functions of the known variables are merely constants. Therefore the third line of the equation is the simplified generative model of interest.

@@

\bibliographystyle{alpha}
\bibliography{sample.bib}
\end{document}
